---
title: "Statistical Inference Project 1"
author: "Robert Tuck"
date: "June 20, 2015"
output: pdf_document
---

### Overview

This project is an investigation of the exponential distribution in R and comparison with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. The investigation uses the distribution of averages of 40 exponentials over a thousand simuations. 

### Simulations

```{r}
number_of_simulations <- 1000
lambda <- 0.2
n <- 40

set.seed(316)

simulations <- matrix(rexp(number_of_simulations * n, rate=lambda), number_of_simulations, n)
simulations_mean <- rowMeans(simulations)
```

### Sample Mean versus Theoretical Mean
```{r}
data_mean <- mean(simulations_mean)
data_mean
theoretical_mean <- 1/lambda
theoretical_mean
```

### Sample Variance versus Theoretical Variance
```{r}
data_variance <- var(simulations_mean)
data_variance
theoretical_var <- ((1/lambda)*(1/sqrt(n)))^2
theoretical_var
```

### Distribution
```{r}
library(ggplot2)
normal_plot_data <- data.frame(simulations_mean)
g <- ggplot(normal_plot_data, aes(x = simulations_mean)) 
g <- g + geom_histogram(alpha = .20, colour = "black", aes(y = ..density..))
g <- g + geom_density(color = "red")
```
```{r}
actual_confidence_interval <- mean(simulations_mean) + c(-1, 1) * qnorm(0.975) * sd(simulations_mean)/sqrt(n)
actual_confidence_interval
theoretical_confidence_interval <- theoretical_mean + c(-1,1) * qnorm(0.975)*sqrt(theoretical_var)/sqrt(n)
theoretical_confidence_interval
```
```{r}
qqnorm(simulations_mean)
qqline(simulations_mean)
```
