---
title: "Statistical Inference Project 1 - Part 2"
author: "Robert Tuck"
date: "June 20, 2015"
output: html_document
---

### Overview
Analysis of the TootGrowth data in the R datasets package.  The ToothGrowth dataset in R is data from a study titled "The Effect of Vitamin C on Tooth Growth in Guinea Pigs".  The data records the length of the teeth in 10 guinea pigs at three levels of Vitamin C (0.5, 1, and 2mg) with thwo delivery methods (orange juice or ascorbic acid)

### Basic Data Summry
```{r}
# load the data
library(ggplot2)
tooth_data <- data.frame(ToothGrowth)
summary(tooth_data)
tooth_data$dose <- as.factor(tooth_data$dose)
ggplot(aes(x=dose, y=len), data=tooth_data) + geom_boxplot(aes(fill=dose))
ggplot(aes(x=supp, y=len), data=tooth_data) + geom_boxplot(aes(fill=supp))
```
### Tests to compare tooth growth by supplement type and dose
Using a t-test to see if supplement type has any effect on tooth growth
```{r}
t.test(len ~ supp, data = tooth_data)
```
The p-value is 0.06, which indicates that the type of supplement likely has no significant effect on tooth growth.

Perform a pair-wise t-test analysis on changes in dosage to see the effect of dose on tooth length
```{r}
doses_0.5_1 <- subset(tooth_data, dose %in% c(0.5, 1))
doses_0.5_2 <- subset(tooth_data, dose %in% c(0.5, 2))
doses_1_2 <- subset(tooth_data, dose %in% c(1, 2))

t.test(len ~ dose, data = doses_0.5_1)
t.test(len ~ dose, data = doses_0.5_2)
t.test(len ~ dose, data = doses_1_2)
```

For all three pairs, the p-value is less than 0.05 and the confidence interval doesn't contain zero.  This indicates that tooth growth increases as dose level increases. 

### Conclusions

1. Supplement type has no effect on tooth growth.
2. Inreasing the dose level leads to increased tooth growth.

### Assumptions

We assume the experiment was performed by randomly assigning guniea pigs to dosage levels and supplement type.
We assume the guniea pigs in this experiment are representative of all guniea pigs.
We assume all of the variances in the groups are equal in the t-tests.